Alleviating the Topology Mismatch Problem in Distributed Overlay Networks: A Survey

### 2015-07-26 mard-survey.tex
2015.07.23 (Alex) Renaming the paper to add the word "survey" in order to better fit JSS. Some minor fixes to author names and affiliations. Adding letter to JSS Editor-In-Chief and submission receipt + other resources.

\title{Alleviating the Topology Mismatch Problem in Distributed Overlay Networks}

@@

\author{Vassilis Moustakas,
        H\"useyin Akcan,
        Mema Roussopoulos,
        and~Alex Delis}

\address{
\emph{vsmoustakas@gmail.com}
\emph{huseyin.akcan@ieu.edu.tr}
\emph{\{mema,ad\}@di.uoa.gr}
}

>>>>

\title{Alleviating the Topology Mismatch Problem in Distributed Overlay Networks: A Survey}

@@

% \author{Vassilis Moustakas,
        % H\"useyin Akcan,
        % Mema Roussopoulos,
        % and~Alex Delis}
% 
% \address{
% Amazon Services\emph{vsmoustakas@gmail.com,}
% Izmir Economics Univ.  \emph{huseyin.akcan@ieu.edu.tr,}
% Univ. of Athens \emph{\{mema,ad\}@di.uoa.gr}
% }

\author[rvt0]{Vassilis Moustakas} % \fnref{fn1}}
\ead{vsmoustakas@gmail.com}
\author[focal]{H\"useyin Akcan} % \fnref{fn2}}
\ead{huseyin.akcan@ieu.edu.tr}
\author[rvt]{Mema Roussopoulos} % \fnref{fn3}}
\ead{mema@di.uoa.gr}
\author[rvt]{Alex Delis\corref{cor1}} % \fnref{fn3}}
\ead{ad@di.uoa.gr}
\cortext[cor1]{Corresponding author}
% \cortext[cor2]{Principal corresponding author}
% \fntext[fn1]{Department of Informatics and Telecommunications, University of Athens, Athens, 15703, Greece.}
% \fntext[fn2]{Department of Software Engineering, Izmir University of Economics, 35330 Balcova, Izmir, Turkey}
% \fntext[fn3]{Yet another author footnote. Indeed, you can have
% any number of author footnotes.}
\address[rvt0]{Amazon Development Center Germany GmbH, Marcel-Breuer Str. 12, 80807 Munich, Germany}
\address[focal]{Department of Software Engineering, Izmir University of Economics, 35330 Balcova, Izmir, Turkey}
\address[rvt]{Department of Informatics and Telecommunications, University of Athens, Athens, 15703, Greece}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
